Monster or Lambda?  A likelihood analysis

### 2023-01-25 inst/monster_vs_lambda.Rmd
better parameter ranges

```{r,tryha3,cache=TRUE}
H <- ha3(D,lambda=1.01)
print(H)
s <- specificp.gt.test(H,"M",0,n=10)  # NB lambda = 1.88
s
```

@@

```{r,label=marginallambdaprofilelike,cache=TRUE}
f <- function(lambda){
 write(date(),file="marginallambdaprofilelike",append=TRUE)  # so we can check its progress
 return(maxp(ha3(D,lambda=lambda),give=TRUE)$value)
}

lam <- seq(from=1.2,to=4.6,len=15)
supp_M_eq_0 <- sapply(lam,f)
```

```{r,plotprofilelikem0}
plot(lam,supp_M_eq_0,type="b",xlab="lambda")
```

@@

```{r,syntheticdataP}
set.seed(0)
P <- matrix(0,4,4)
teams <- LETTERS[1:4]
dimnames(P) <- list("@home" = teams,"@away"=teams)
P
n <- 2000 # number of matches between a pair 
M <- 0.0005  # home monster
strengths <- 1/(1:4) # Zipf
strengths <- strengths/sum(strengths)
names(strengths) <- teams
strengths
for(home_team in 1:4){
  for(away_team in 1:4){
    if(home_team != away_team){
      prob_home_win <- (strengths[home_team] + M)/(strengths[home_team] + strengths[away_team] + M)
      home_wins <- rbinom(1,n,prob_home_win)
      home_losses <- n - home_wins
      P[home_team,away_team] <- home_wins + 1i*home_losses
    }
  } 
}
diag(P) <- NA
P
HP <- home_away(P)
```

@@

```{r,label=maxpmonsteqq,cache=TRUE}
mH <- maxp(HP,n=3,give=T)
mH
```

>>>>

```{r,tryha3,cache=TRUE}
H <- ha3(D,lambda=1.01)
print(H)
```

```{r,maxha3,cache=TRUE}
maxp(H)
```

```{r,testha3,cache=TRUE}
s <- specificp.gt.test(H,"M",0,n=10)  # NB lambda = 1.88
s
```

@@

```{r,label=marginallambdaprofilelike,cache=TRUE}
write(date(),file="marginallambdaprofilelike",append=FALSE)
f <- function(lambda){
 write(date(),file="marginallambdaprofilelike",append=TRUE)  # so we can check its progress
 return(maxp(ha3(D,lambda=lambda),n=1,give=TRUE)$value)
}

lam <- seq(from=0.1,to=4.2,len=5)
supp_M_eq_0 <- sapply(lam,f)
```

```{r,plotprofilelikem0}
plot(lam,supp_M_eq_0,type="b",xlab="lambda")
plot(lam,supp_M_eq_0-max(supp_M_eq_0),type="b",xlab="lambda")
grid()
abline(h=c(0,-2))
```

@@

```{r,syntheticdatapp}
set.seed(0)
P <- matrix(0,4,4)
teams <- LETTERS[1:4]
dimnames(P) <- list("@home" = teams,"@away"=teams)
P
n <- 400 # number of matches between a pair 
M <- 0.15  # home monster
strengths <- 1/(1:4) # Zipf
strengths <- strengths/sum(strengths)
names(strengths) <- teams
strengths
for(home_team in 1:4){
  for(away_team in 1:4){
    if(home_team != away_team){
      prob_home_win <- (strengths[home_team] + M)/(strengths[home_team] + strengths[away_team] + M)
      home_wins <- rbinom(1,n,prob_home_win)
      home_losses <- n - home_wins
      P[home_team,away_team] <- home_wins + 1i*home_losses
    }
  } 
}
diag(P) <- NA
P
HP <- home_away(P)
```

@@

```{r,label=maxpmonsteq1,cache=TRUE}
mH <- maxp(HP,n=3,give=T)
mH
```

```{r proflikesyntha,cache=TRUE}
home <- seq(from=0.12,to=0.16,len=15)
supp_lambda_eq_0 <- profsupp(HP,"home",home,relative=FALSE)
```

```{r plotsynthprof}
plot(home,supp_lambda_eq_0,type='b')
plot(home,supp_lambda_eq_0 - max(supp_lambda_eq_0),type='b')
abline(h=c(0,-2))

```{r marginalsynthcalct,cache=TRUE}
f <- function(lambda){
 return(maxp(ha3(P,lambda=lambda),n=1,give=TRUE)$value)
}

lam <- seq(from=0.5,to=1.3,len=7)
supp_M_eq_0 <- sapply(lam,f)
```

```{r plotsynthma}
plot(lam,supp_M_eq_0,type='b')
plot(lam,supp_M_eq_0-max(supp_M_eq_0),type='b')
abline(h=c(0,-2))
```

```{r plotbothtogether}
jj <- c(supp_M_eq_0,NA,supp_lambda_eq_0)
plot(jj-max(jj,na.rm=TRUE),type="b")
abline(h=c(0,-2))
```
